### 2019-02-25 manuscript/results.tex
wording edit
Fixing a request from Boris that snuck in when I wasn't looking.

%B: The "For X (states model), we found" template doesn't sound quite right to me. Maybe, "Fitting" or "Considering" or "When" (as in second portion with hidden-state model. In latter case, possibly (1) When considering X alone..., (2) Addition of... / Incorporating a hidden state...
%
For ploidy alone (D/P model), we found a greater net diversification rate for diploids than for polyploids, in agreement with \citep{mayrose_2011, mayrose_2015}.
This result holds with (\cref{figure:netdivall}A) or without (\cref{figure:netdivnodip}A) the diploidization parameter, though including diploidization shifts the net diversification rate of polyploids to be non-negative.
Incorporating a hidden state, however, removes the clear separation in diversification between diploids and polyploids (D/P+A/B model; \cref{figure:netdivall}B, \cref{figure:netdivnodip}B).
Thus, differences in net diversification are better explained by an unknown factor than by ploidy.
Statistical model comparisons show very strong support for including the hidden state and strong support for including diploidization (\cref{table:bayesfactors}).
% E: I removed the description of relative extinction results.  We don't discuss it for other models or show it in the main text, and I never really know what to make of that compound parameter.  But it's good that it's in the supp info.

For breeding system alone, we found a larger net diversification rate for SI than for SC species, in agreement with \citet{goldberg_2010} (I/C model, \cref{figure:netdivall}C).
When a hidden state is included (I/C+A/B model), the large net diversification difference persists for one of the hidden states but is removed for the other (\cref{figure:netdivall}D).
Thus, differences in net diversification are best explained by both breeding system and an unknown factor.
% The transition rate from SI to SC is $q_{IC}=0.3$ for both the I/C and the I/C+A/B models.
The statistical model comparison shows very strong support for including the hidden state (\cref{table:bayesfactors}).

For ploidy and breeding system together (ID/CD/CP model), the net diversification rate for SI diploids was greater than for either SC diploids or SC polyploids, with or without diploidization (\cref{figure:netdivall}E, \cref{figure:netdivnodip}C).
It thus appears that the difference in net diversification with breeding system persists when ploidy is included in the model, but not the reverse.
The association of ploidy with net diversification in the D/P model (\cref{figure:netdivall}A, \cref{figure:netdivnodip}A) appears to be driven by the subset of diploids that are SI; among SC species, net diversification rates for diploids and polyploids are similar.
%
When a hidden state is included (IC/CD/CP+A/B model), the same general pattern remains when diploidization is prevented (\cref{figure:netdivnodip}D), although the higher net diversification rate of ID is less clear within one of the hidden states.
With diploidization, the net diversification rate of ID is still greater than CD within each hidden state, but diversification for P is highly uncertain and perhaps bimodal.
Statistical model comparisons show very strong support for including the hidden state and at most positive support for including diploidization (\cref{table:bayesfactors}).

% E: I moved the discussion of \rho_I and \rho_C values into the Pathways section.
% E note to self: keep editing from here XXX

>>>>

When considering ploidy alone (D/P model), we found a greater net diversification rate for diploids than for polyploids, in agreement with \citep{mayrose_2011, mayrose_2015}.
This result holds with (\cref{figure:netdivall}A) or without (\cref{figure:netdivnodip}A) the diploidization parameter, though including diploidization shifts the net diversification rate of polyploids to be non-negative.
Incorporating a hidden state, however, removes the clear separation in diversification between diploids and polyploids (D/P+A/B model; \cref{figure:netdivall}B, \cref{figure:netdivnodip}B).
Thus, differences in net diversification are better explained by an unknown factor than by ploidy.
Statistical model comparisons show very strong support for including the hidden state and strong support for including diploidization (\cref{table:bayesfactors}).
% E: I removed the description of relative extinction results.  We don't discuss it for other models or show it in the main text, and I never really know what to make of that compound parameter.  But it's good that it's in the supp info.

When considering breeding system alone, we found a larger net diversification rate for SI than for SC species, in agreement with \citet{goldberg_2010} (I/C model, \cref{figure:netdivall}C).
When a hidden state is included (I/C+A/B model), the large net diversification difference persists for one of the hidden states but is removed for the other (\cref{figure:netdivall}D).
Thus, differences in net diversification are best explained by both breeding system and an unknown factor.
% The transition rate from SI to SC is $q_{IC}=0.3$ for both the I/C and the I/C+A/B models.
The statistical model comparison shows very strong support for including the hidden state (\cref{table:bayesfactors}).

When considering ploidy and breeding system together (ID/CD/CP model), the net diversification rate for SI diploids was greater than for either SC diploids or SC polyploids, with or without diploidization (\cref{figure:netdivall}E, \cref{figure:netdivnodip}C).
It thus appears that the difference in net diversification with breeding system persists when ploidy is included in the model, but not the reverse.
The association of ploidy with net diversification in the D/P model (\cref{figure:netdivall}A, \cref{figure:netdivnodip}A) appears to be driven by the subset of diploids that are SI; among SC species, net diversification rates for diploids and polyploids are similar.
%
When a hidden state is included (IC/CD/CP+A/B model), the same general pattern remains when diploidization is prevented (\cref{figure:netdivnodip}D), although the higher net diversification rate of ID is less clear within one of the hidden states.
With diploidization, the net diversification rate of ID is still greater than CD within each hidden state, but diversification for P is highly uncertain and perhaps bimodal.
Statistical model comparisons show very strong support for including the hidden state and at most positive support for including diploidization (\cref{table:bayesfactors}).

% E: I moved the discussion of \rho_I and \rho_C values into the Pathways section.

% E note to self: keep editing from here XXX
